Rotation effects on the Lyman-$\alpha$ line morphology in distant galaxies

### 2013-05-22 paper/Analisis.tex
First draft in the Integrated Flux section

\begin{figure*}
    \includegraphics[width=0.45\textwidth]{maximumvscosthetaHOMSameSpeed.png}
    \includegraphics[width=0.45\textwidth]{maximumvscosthetaDifSpeedCentral.png}
\caption{Position of the maxima
    in the outgoing spectra for differents Rotational velocities,
    (up)Central Distriution, (Down) Homogeneous Distribution.\label{fig:maximumsvsvelocity}} 
\end{figure*}

@@

..compare steidel et al (2011)

@@

... The results derived in this paper have consequences on the
interpreation of galaxy observations in the Lyman alpha line.
% taking into account equivalent widths results with narrow band
% filters we can make a criterium in order to select wich galaxie
% could be seen in actual observations.

>>>>

%\begin{figure*}
%    \includegraphics[width=0.45\textwidth]{maximumvscosthetaHOMSameSpeed.png}
%    \includegraphics[width=0.45\textwidth]{maximumvscosthetaDifSpeedCentral.png}
%\caption{Position of the maxima
%    in the outgoing spectra for differents Rotational velocities,
%    (up)Central Distriution, (Down) Homogeneous Distribution.%\label{fig:maximumsvsvelocity}} 
%\end{figure*}

@@

Untill now we have shown the main effects of gas and dust rotation in the Ly$\alpha$ line morphology such as the escape fraction, the FWHM the maxima position and the effect of the position of an observer. It is important to see if rotational effects are detectable in observational methods involving the Ly$\alpha$ line. By far this is not and extensive study, it is just and ....

One of the most used methods to detect high redshift galaxies using the Ly$\alpha$ line is using a narrowband selection, this implies..(explain a lit of bit the method)

We make this analysis based in the results obtained by Steidel (2011) in this work (EXPLAIN a lit of bit more about their work) they used tree narrowband filters for tree different redshifts resumed in Table~\ref{table:NBfilters}, We want to know how much the integrated flux change due to rotational effects in this NB filters, for the models we simulated with CLARA.

\begin{table}
\begin{center}
\begin{tabular}{cccc}\hline
Model & SSA22a 4980/80  & HS1700 4018/90 & HS1549 4667/80\\
\hline
V0HOM & 99965 / 98658 / & &\\
V100HOM & 99221 / 95517 / 75058 & &\\
V200HOM & 90630 / 90630 / 73938 & &\\
V300HOM & 82180 / 82180 / 71953 & &\\
V0HOMDust & 99968 / 99798 / 93132 & &\\
V100HOMDust & 99445 / 98579 / 91208 & &\\
V200HOMDust & 91439 / 90723 / 86134 & &\\
V300HOMDust & 83116 / 82630 / 79943 & &\\
\hline
\end{tabular}
\caption{
Values of fluxes for tree different NB and the our models simulated with CLARA
} 
\label{table:NBfilters}
\end{center}
\end{table}

As a first approach we may see that

@@

... The results derived in this paper have consequences on the
interpreation of galaxy observations in the Lyman alpha line.
..compare steidel et al (2011)
% taking into account equivalent widths results with narrow band
% filters we can make a criterium in order to select wich galaxie
% could be seen in actual observations.
